A Geometry for Network Visualization in \MakeLowercase{\texttt{ggplot2}}

### 2015-03-11 CC/writeup.Rnw
couple of references included

\documentclass[11pt]{article}
\usepackage{xspace}
\usepackage{geometry} % see geometry.pdf on how to lay out the page. There's lots.
\geometry{a4paper} % or letter or a5paper or ... etc
% \geometry{landscape} % rotated page geometry
% See the ``Article customise'' template for come common customisations

\title{A Geometry for Network Visualization in \MakeLowercase{\texttt{ggplot2}}}
\author{Sam Tyner and Heike Hofmann}
\date{} % delete this line to display the current date

%%% BEGIN DOCUMENT
\begin{document}

\maketitle

\section{Introduction}
\par The three necessary elements of any network visualization are the vertices, the edges, and the layout.  But once those three items are visualized, we usually find our visualization to be lacking.  We may want to color the vertices (or edges) by some sort of grouping variable, or we may want to make vertices of degree 10 twice the size of vertices of degree 5.  Many \texttt{R} packages already exist for network analysis and visualization such as \texttt{igraph} by Gabor Csardi, \texttt{sna} by Carter T. Butts, and \texttt{network} by Carter T. Butts et al. but we have found these packages to have unintuitive or burdensome methods for customizing the colors, sizes, etc of the vertices and edges of the network. For instance, the \texttt{igraph} package allows for coloring vertices by groups but the user must assign the colors to each vertex individually as opposed to assigning color by a grouping factor variable. \\

@@

>>>>

\documentclass[11pt]{article}
\usepackage{asa}
\usepackage{xspace}
\usepackage{natbib}
\usepackage{geometry} % see geometry.pdf on how to lay out the page. There's lots.
\geometry{a4paper} % or letter or a5paper or ... etc
% \geometry{landscape} % rotated page geometry
% See the ``Article customise'' template for come common customisations

%\definecolor{Blue}{rgb}{0,0,0.5}
\newcommand{\hh}[1]{{\color{magenta} #1}}
\newcommand{\sct}[1]{{\color{purple} #1}}

\title{A Geometry for Network Visualization in \MakeLowercase{\texttt{ggplot2}}}
\author{Sam Tyner and Heike Hofmann}
\date{} % delete this line to display the current date
%%% BEGIN DOCUMENT
\begin{document}

\maketitle
\begin{abstract}
Abstract will be here
\end{abstract}

\section{Introduction}
\par The three necessary elements of any network visualization are the vertices, the edges, and the layout.  But once those three items are visualized, we usually find our visualization to be lacking.  We may want to color the vertices (or edges) by some sort of grouping variable, or we may want to make vertices of degree 10 twice the size of vertices of degree 5.  Many \texttt{R} packages already exist for network analysis and visualization such as \texttt{igraph} by \citet{igraph}, \texttt{sna} by \citet{sna}, and \texttt{network} by \citet{network.jss, network} but we have found these packages to have unintuitive or burdensome methods for customizing the colors, sizes, etc of the vertices and edges of the network. For instance, the \texttt{igraph} package allows for coloring vertices by groups but the user must assign the colors to each vertex individually as opposed to assigning color by a grouping factor variable. \\

@@

\bibliographystyle{asa}
\bibliography{references}
